---
title: "Joins with singer"
author: "Joey Bernhardt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Joins with singer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```


This vignette will demonstrate the use of `dplyr` joins. We will use two small dataframes, `songs` and `locations` to explore different types of joins.


```{r, warning=FALSE}
library(singer)
library(tidyverse)

data(songs)
data(locations)

```




#### inner_join(songs, locations)

> inner_join(x, y): Return all rows from x where there are matching values in y, and all columns from x and y. If there are multiple matches between x and y, all combination of the matches are returned. This is a mutating join.

```{r}
ijsl <- inner_join(songs, locations)
knitr::kable(ijsl)
```


#### semi_join(songs, locations)

> semi_join(x, y): Return all rows from x where there are matching values in y, keeping just columns from x. A semi join differs from an inner join because an inner join will return one row of x for each matching row of y, where a semi join will never duplicate rows of x. This is a filtering join.

```{r}
sjsl <- semi_join(songs, locations)
knitr::kable(sjsl)
```

